Reproducible research: A tutorial about doing the same thing more than once in R

### 2021-08-04 manuscript.Rmd
alternative title suggestion

title: A Hitchhiker's Guide to Reproducible Research in R

@@

````markdown
---
title: A Hitchhiker's Guide to Reproducible Research in R
author: Aaron Peikert, Caspar J. Van Lissa and Andreas M. Brandmaier
abstract: A tutorial about doing the same thing more than once.
output: html_document
---

@@

```markdown
---
title: A Hitchhiker's Guide to Reproducible Research in R
author: Aaron Peikert, Caspar J. Van Lissa and Andreas M. Brandmaier
abstract: A tutorial about doing the same thing more than once.
output: html_document
repro:
  scripts:
    - R/load.R
  data:
    - data/mtcars.csv
  packages:
    - tidyverse
    - usethis
    - gert
---
```

>>>>

title: "Reproducible research: A tutorial about doing the same thing more than once in R"

@@

````markdown
---
title: "Reproducible research: A tutorial about doing the same thing more than once in R"
author: Aaron Peikert, Caspar J. Van Lissa and Andreas M. Brandmaier
abstract: A Hitchhiker's Guide to Reproducible Research in R
output: html_document
---

@@

```markdown
---
title: "Reproducible research: A tutorial about doing the same thing more than once in R"
author: Aaron Peikert, Caspar J. Van Lissa and Andreas M. Brandmaier
output: html_document
repro:
  scripts:
    - R/load.R
  data:
    - data/mtcars.csv
  packages:
    - tidyverse
    - usethis
    - gert
---
```
